Mapping plant-pollinator interactions across Europe

### 2023-12-12 Manuscript/Ms.qmd
Updating author list from Hervias-Parejo

```{r Load libraries, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(giscoR)
library(sf)
```
# Abstract

Pollinators play a crucial role in maintaining Earth's terrestrial biodiversity and human food production by mediating sexual reproduction for most flowering plants. However, their diversity and role as pollinators are increasingly compromised by rapid human-induced environmental changes. One of the major challenges for pollinator conservation, is the lack of robust generalisable data across space and time. Here, we present a dataset of plant-pollinator interactions at European level that consists in XXX studies compiled during the years xxx and xxxx.

>>>>

```{r Load libraries, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(giscoR)
library(sf)
```

# Abstract

Pollinators play a crucial role in maintaining Earth's terrestrial biodiversity and human food production by mediating sexual reproduction for most flowering plants. However, their diversity and role as pollinators are increasingly compromised by rapid human-induced environmental changes. One of the major challenges for pollinator conservation, is the lack of robust generalisable data across space and time. Here, we present a dataset of plant-pollinator interactions at European level that consists of `r study_number` studies compiled during the years xxx and xxxx.
